\documentclass[11pt]{article}

\usepackage{hyperref}\usepackage{titling}
\usepackage[top=1in, bottom=1in, left=1in, right=1in]{geometry}


\title{\textsc{\textbf{Software Radio Implementation Forum (SRIF) 2015}}}

\preauthor{}\postauthor{}\author{}
\predate{}\postdate{}\date{}


\begin{document}

\maketitle


\section{Call for Papers}

The Software Radio Implementation Forum seeks papers for the SRIF 2015
workshop to be held September 7, 2015 at ACM MobiCom in Paris.

Bringing together researchers and practitioners of software defined
radio (SDR), the SRIF seeks to understand the innovative and practical
applications of SDR technology, explore the challenges of
implementation, and research the gap between our goals and the reality
of system deployments. Through this exchange, the workshop aims to
facilitate collaborations between academia and industry to address
these areas of interest. The workshop is a venue for industrial
participants to share their experiences and best practices for
commercial deployments of SDR systems and for researchers to share
their latest results in new applications and designs.

We invite paper, poster, and demo submissions in all areas related to
SDR development and research. Example topics of interest include:

\begin{itemize}
\item Hardware and software architectures for software radio
\item Virtualization technologies for radio resources
\item WLAN, LTE, and 5G networks
\item Millimeter wave challenges
\item Challenges and opportunities in space
\item Prototypes of novel wireless systems using SDR
\item State-of-the-art performance of wireless systems using SDR
\item PHY and MAC primitives and abstractions
\item Programming models for SDR
\item New applications for SDR (e.g., security, localization, medical, etc.)
\item New insights on wireless theory vs. practice enabled by SDR
\end{itemize}


\section{Technical Talks}

A full-length paper (max 6 pages, double-column) is required for all
technical talks. Submitted papers will be reviewed and published in a
workshop proceedings. Depending on the number of submissions, some
papers may be allocated to the poster session for presentation
purposes. Papers allocated to the poster session will still be
published in the workshop proceeding. The proceeding is expected to be
indexed by EI and/or ACM, IEEE.


\section{Poster Presentations and Demonstrations}

Full-length papers (max 6 pages, double-column) are optional. Without
a full-length paper, an abstract/summary of no more than one page in
length is required. All accepted papers and abstracts will be
published in the workshop proceeding.



\section{Important Dates}

\begin{itemize}
\item May 15, 2015: Paper/extended abstract submission deadline
\item June 8, 2015: Acceptance notification
\item July 3, 2015: Camera-ready due
\item August 14, 2015: Program available online
\end{itemize}



\section{Contact}

Please contact SRIF 2015 general chair Li Erran Li
(erranlli@gmail.com) with any inquiries.


\end{document}
